On the eletrodynamic of moving bodies

### 2019-05-27 Article_AS.Rmd
Modif intro

---
title: "On the eletrodynamic of moving bodies"
author: "André Dogninema Soro, Jean-Romain Roussel, Alexis Achim"
editor_options:
  chunk_output_type: inline
output: pdf_document
bibliography: biblio.bibtex
---

@@

Canadian forest is an important part of the country's history, culture, natural environment and economy. But thousands of hectares of canadian forest are harvested each year and an additionnal loss is due to insects, diseases and fires [@DRF2000; @NaturalResourcesCanada2019]. To maintain ressource constant, it is therefore essential to compensate the sampling and the looses by reforesting. The reforestation, when under human control, could ideally be made by using better trees than the former ones, i.e. trees that growth faster, that are more resistant to perturbation and that are of better stuctural quality. To achieve this task, we must take into account the cambial activity that is governed by environmental conditions and genetics [@Dufour2010; @Rossi2012]. Therefore, genetic selection is one of the available tools and is currently becoming a crucial and increasingly necessary for the development of the canadian forest [@Bonfils2004]. It allows to select trees with characters of interest and to cross them or to reproduce them in order to obtain trees with interesting properties for the development of the forests or the quality of the wood for the human use. \

Improvement programs by genetic selection are in place for the most important commercial species [@DRF2000; @Mullin2011] including white spruce (Picea glauca (Moench) Voss) which has a significant economic value because of its geographical distribution and abundance [@Eyre1980; @Abrahamson2015]. Spruce wood is valuable as lumber, material for carpentry products and for pulping because of the characteristics of its fibres [@Zhang2008]. In addition, the plasticity of spruce, enable this species to adapt to various types of soil and climatic conditions [@Nienstaedt1990]. All these characteristics make white spruce a species of great interest in North America and consequently it is heavily reforested in various silvicultural systems in Canada with more than 150 million of natural an hybrid seedlings planted yearly accross almost all forested regions which represents a wide range of soils types and a climatic conditions (Canadian Council of Forest Ministers 2009). \

During the first half of the 20th century, most studies about genetic selection were dedicated on increasing wood volume production [@Dhir1976; @nienstaedt1985; @Li1997; @Koubaa2000] but with the increasing demand of high structural quality products and the fear of lossing ressource from natural causes, the aspects of wood quality became as important as wood volume [@Franceschini2012]. Conifer breeding programs are more and more considering wood quality as selection criteria to improve end-use properties. Wood density is among the key traits as it is related mechanical strength and dimensional stability. Variation in density within a piece of wood may lead to deformation during transformation and inhomogeneous machining properties. Consequently studies have been set up to understand the genetic sources of phenotypic variations of wood quality [@Corriveau1971; @Li1993; @Hernandez2001; @Beaulieu2003; @Lenz2013; @McLean2016]. For example, future genetic selections in breeding programs for different species of spruce trees in Quebec will consider wood properties such as wood density [@Mullin2011, @Beaulieu2009]. Wood quality has mainly two components: biologic and economic. The biologic component is the resistance to mortality by vigor and the economic component is the value of the wood for end-use. Several traits were considered for wood quality assessment and the density is one of the most widely used indicators and arguably the most important one [@zobel1989; @Saranpaa1994; @Mckendry2002; @Macdonald2002; @Alteyrac2006] because this trait is important for both components of quality and strongly correlated with different mechanical and anatomical wood traits [@zobel1989]. \

With regard to the biological component, in has been demonstrated [@Hietz2013, @osazuwa2014] that trees with a more uniform wood densitiy within the stem are also the more resistant to mortality. For example a uniform density gives a greater mechanical resistance to the wind and therefore a lower probability of mortality during a climatic event such as a storm. With regard to the economical context, uniformity affects the performance of saw timber, the pulp yield and calorific values for biomass applications for bioenergy [@Hernandez2001; @Macdonald2002; @Mckendry2002]. For exemple, a strong interannual variation of the density of the wood leads to a decrease of the mechanical resistance while a relatively uniform density produce wood with better mechanical performance. It is therefore important from both a biological point of view and a end-use point of view to have a wood with a uniform density within the stem. \

From these studies we understand that there might be a strong gain at selecting trees that are prone to produce wood of uniform density to get a resistant and higly valuable forest in the next decades. To reach this goal is is important to understant where do the variations of density come from. In white spruce, there is a typical low frequency radial pattern of variation from pith to bark [@Moore2011]. First a decrease of density during the first years of growth and then an increase from the beginning of the formation of mature wood [@panshin1980]. In addition this radial variations there are hight frequency interannual variation [@Nicault2010]. Contrary to the radial variation that is under internal control, the interannual variation of the density is influenced mainly by events events to the tree such as the edaphic and climatic conditions [@Nicault2010] that happen at high frequency. \

Unlike growth that is more controlled by environment than genetic and therefore has low to moderate heritability [@Ivkovich2002a], wood density in white spruce is under strong genetic control with moderate to high heritability [@Corriveau1991; @Yanchuk1993; @Ivkovich2002a; @Ivkovich2002b, @Beaulieu2006] and this makes this trait attractive for genetic improvement. Moreover, Climate is a determining factor for the growth and physiological processes of trees. As a result, climatic conditions strongly affect the properties of wood. In fact, certain climatic factors such as drought can cause stress in trees and cause a variation in wood properties, including density, ring width and conductivity. In addition, long-term growth analyzes have shown that it may increase due to temperature, atmospheric CO2 content and nitrogen deposition [@becker1995; @huang2007; @zaehle2014]. Knowing that density can be negatively correlated with growth in spruce [@zhang1995], it is essential to take this factor into account.

However, the timeframe of such improved forest management being long [@Zobel1972] it is essential to take into account the current climate change context [@Gray2016]. With the increasing temperature, the trees are expected to growth faster and thus being of lower quality because of lower density [@corriveau1987; @DeBell1994; @Lindstrom1996; @Dutilleul1998; @Bouriaud2005]. It is necessary to anticipate the possible environmental variations because more important frequencies water stress or important precipitations are feared with the climatic changes [@IPCC2007; @pachauri2014]. These environmental variations may lead to an increase or decrease in radial growth and thus cause greater variations in the density of the wood. In addition to selecting trees that are prone to produce wood of uniform density we must also ensure that these properties will persist in time with climatic change. Thus the selection must also considered the stability of the properties in time or, more accuralty, with climate change. The heritability of density has been proven in several studies, but there is no evidence to suggest that density variability is hereditary. The heritability of this trait could qualify it for the selection criteria for future breeding programs for producing better quality wood.\

>>>>

---
title: "On the eletrodynamic of moving bodies"
author: "André Dogninema Soro, Jean-Romain Roussel, Alexis Achim"
editor_options:
  chunk_output_type: inline
output:
  pdf_document: default
  word_document: default
bibliography: biblio.bibtex
---

@@

Canadian forest is an important part of the country's history, culture, natural environment and economy. But thousands of hectares of canadian forest are harvested each year and an additionnal loss is due to insects, diseases and fires [@DRF2000; @NaturalResourcesCanada2019]. To maintain ressource constant, it is therefore essential to compensate the sampling and the looses by reforesting. The reforestation, when under human control, could ideally be made by using better trees than the former ones, i.e. trees that growth faster, that are more resistant to perturbation and that are of better stuctural quality. To achieve this task, we must take into account the cambial activity that is governed by environmental conditions and genetics [@Dufour2010; @Rossi2012]. Therefore, genetic selection is one of the available tools and is currently becoming a crucial and increasingly necessary for the development of the canadian forest [@Bonfils2004]. It allows to select trees with characters of interest and to cross them or to reproduce them in order to obtain trees with interesting properties for the development of the forests or the quality of the wood for the human use. \ 
Improvement programs by genetic selection are in place for the most important commercial species [@DRF2000; @Mullin2011] including white spruce (Picea glauca (Moench) Voss) which has a significant economic value because of its geographical distribution and abundance [@Eyre1980; @Abrahamson2015]. Spruce wood is valuable as lumber, material for carpentry products and for pulping because of the characteristics of its fibres [@Zhang2008]. In addition, the plasticity of spruce, enable this species to adapt to various types of soil and climatic conditions [@Nienstaedt1990]. All these characteristics make white spruce a species of great interest in North America and consequently it is heavily reforested in various silvicultural systems in Canada with more than 150 million of natural an hybrid seedlings planted yearly accross almost all forested regions which represents a wide range of soils types and a climatic conditions [@Canadian2009]. \

During the first half of the 20th century, most studies about genetic selection were dedicated on increasing wood volume production [@Dhir1976; @nienstaedt1985; @Li1997; @Koubaa2000] but with the increasing demand of high structural quality products and the fear of lossing ressource from natural causes, the aspects of wood quality became as important as wood volume [@Franceschini2012]. Therefore, conifer breeding programs are more and more considering wood quality as selection criteria to improve end-use properties. Wood quality has mainly two components: biologic and economic. The biologic component is the resistance to mortality by vigor and the economic component is the value of the wood for end-use. Several traits were considered for wood quality economic and the density is one of the most widely used indicators and arguably the most important one [@zobel1989; @Saranpaa1994; @Mckendry2002; @Macdonald2002; @Alteyrac2006] because this trait is important for both components of quality and strongly correlated with different mechanical (mechanical resistance and the dimensional stability) and anatomical wood traits [@zobel1989]. Thus, variation in density within a piece of wood may lead to deformation during transformation and inhomogeneous machining properties. Consequently studies have been set up to understand the genetic sources of phenotypic variations of wood quality [@Corriveau1971; @Li1993; @Hernandez2001; @Beaulieu2003; @Lenz2013; @McLean2016]. For example, future genetic selections in breeding programs for different species of spruce trees in Quebec will consider wood properties such as wood density [@Mullin2011; @Beaulieu2009]. 
With regard to the biological component, in has been demonstrated [@Hietz2013; @osazuwa2014] that trees with a more uniform wood densitiy within the stem are also the more resistant to mortality. For example a uniform density gives a greater mechanical resistance to the wind and therefore a lower probability of mortality during a climatic event such as a storm. With regard to the economical context, uniformity affects the performance of saw timber, the pulp yield and calorific values for biomass applications for bioenergy [@Hernandez2001; @Macdonald2002; @Mckendry2002]. For exemple, a strong interannual variation of the density of the wood leads to a decrease of the mechanical resistance while a relatively uniform density produce wood with better mechanical performance. It is therefore important from both a biological point of view and a end-use point of view to have a wood with a uniform density within the stem. \

In view of the studies cited aboves, we understand that there might be a strong gain at selecting trees that are prone to produce wood of uniform density to get a resistant and higly valuable forest in the next decades. To reach this goal is important to understant where do the variations of density come from. In white spruce, there is a typical low frequency radial pattern of variation from pith to bark [@Moore2011]. First a decrease of density during the first years of growth and then an increase from the beginning of the formation of mature wood [@panshin1980]. In addition, this radial variations there are hight frequency interannual variation [@Nicault2010]. Contrary to the radial variation that is under internal control, the interannual variation of the density is influenced mainly by events events to the tree such as the edaphic and climatic conditions [@Nicault2010] that happen at high frequency. \

Unlike growth that is more controlled by environment than genetic and therefore has low to moderate heritability [@Ivkovich2002a], wood density in white spruce is under strong genetic control with moderate to high heritability [@Corriveau1991; @Yanchuk1993; @Ivkovich2002a; @Ivkovich2002b; @Beaulieu2006] and this makes this trait attractive for genetic improvement. Moreover, Climate is a determining factor for the growth and physiological processes of trees. As a result, climatic conditions strongly affect the properties of wood. In fact, certain climatic factors such as drought can cause stress in trees and cause a variation in wood properties, including density, ring width and conductivity. In addition, long-term growth analyzes have shown that it may increase due to temperature, atmospheric CO2 content and nitrogen deposition [@becker1995; @huang2007; @zaehle2014]. Knowing that density can be negatively correlated with growth in spruce [@zhang1995], it is essential to take climat factor into account.

The timeframe of improved forest management being long [@Zobel1972] it is essential to take into account the current climate change context [@Gray2016]. With the increasing temperature, the trees are expected to growth faster and thus being of lower quality because of lower density [@corriveau1987; @DeBell1994; @Lindstrom1996; @Dutilleul1998; @Bouriaud2005]. It is necessary to anticipate the possible environmental variations because more important frequencies water stress or important precipitations are feared with the climatic changes [@IPCC2007; @pachauri2014]. These environmental variations may lead to an increase or decrease in radial growth and thus cause greater variations in the density of the wood. In addition to selecting trees that are prone to produce wood of uniform density we must also ensure that these properties will persist in time with climatic change. Thus the selection must also considered the stability of the properties in time or, more accuralty, with climate change. furthermore, heritability of density has been proven in several studies, but there is no evidence to suggest that density variability is hereditary. The heritability of this trait could qualify it for the selection criteria for future breeding programs for producing better quality wood.\
